\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-21 coq-example.tex
Reply the comments.

And at the end, the compiled module for "LangTyping" and "LangCP" is put into tests over simple queries. These "LangTyping" and "LangCP" also illustrates that we still have
computability in the presence of family.\YZ{Mention the alternative approach of using parameterized modules.}

@@

Then we provide an overridable predicate \mintinline{Coq}{alg_is_prog : strs -> Type}, decidable provided the inductive hypothesis and sound \& complete w.r.t. to the specification \mintinline{Coq}{alg_is_prog e  <-> is_prog e}. We require extension to take care of the soundness \& completeness and the conditional decidablity.

Among them, completeness \mintinline{Coq}{is_prog e -> alg_is_prog e} is the most challenging part. This is proved by recursion on the predicate "is_prog e", but most of the handler on "is_prog" will not be reused because \mintinline{Coq}{alg_is_prog e} is overriden during inheritance. Unlike completeness, other parts of the construction, including soundness and and conditional decidability can be reused easily.

>>>>

And at the end, the compiled module for "LangTyping" and "LangCP" is put into tests over simple queries. These "LangTyping" and "LangCP" also illustrates that we still have
computability in the presence of family.\YZ{Mention the alternative approach of using parameterized modules.}\EDJreply{What. I don't have that version. My earlier version without family is not extensible, just a POC to see if the proof idea itself is correct.}

@@

Then we provide an overridable predicate \mintinline{Coq}{alg_is_prog : strs -> Type},\YZ{Why does it need to be overridden?}\EDJreply{Basically alg_is_prog is a big disjunction list, corresponding to each of the constructor of }
decidable provided the inductive hypothesis and sound \& complete w.r.t. to the specification \mintinline{Coq}{alg_is_prog e  <-> is_prog e}.  "alg_is_prog e" will be a big disjunction, of which each disjunct $P_i$ corresponds to the argument of one constructor of "is_prog" (each CFG rule). Thus once "is_prog" is extended, we need to disjunct "alg_is_prog" with more condition, thus overridable.  We require extension to take care of the disjuncts, their soundness \& completeness and the conditional decidablity.

Among them, completeness \mintinline{Coq}{is_prog e -> alg_is_prog e} is
the most challenging part. This is proved by recursion on the predicate
"is_prog e", but none of the handler on "is_prog" will be reused
because \mintinline{Coq}{alg_is_prog e} is overriden during
inheritance.\YZ{
    If alg_is_prog e is overridden, then how can ANY handler be reused?
}\EDJreply{You are right. I rephrase into ``none of the handlers''.}
Unlike completeness, other parts of the construction, including
soundness and and conditional decidability can be reused easily.
\YZ{But is the reusability achieved through a derived family's reusing handlers in the base family? Doesn't sound like it because the induction seems to be on strs.}\EDJreply{to prove something like alg_is_prog e -> is_prog e is not doing induction on string. It is just unfolding definition. \\ 
alg_is_prog is a big disjunction, alg_is_prog e = p1 e \/ p2 e\/ ..., and during overriding this disunction list is increasing. \\
So we organize the program by proving ``p1 e -> is_prog e'', ``p2 e -> is_prog e''. Everytime this disjunction list is increasing during overriding, the old proof ``p1 e -> is_prog e'' is reused in the new .}
